SpatialEpi

### 2018-06-02 README.Rmd
About to release on CRAN
Update README

We run the Bayesian Cluster Detection method from Wakefield and Kim (2013)

@@

```{r, cache=TRUE, fig.height=6.5}
plotmap(output$post_map$high_area, sp.obj)
```

>>>>

We run the Bayesian Cluster Detection method from [Wakefield and Kim (2013)](https://www.researchgate.net/publication/235896508_A_Bayesian_model_for_cluster_detection):

@@

```{r, fig.height=6.5}
plotmap(output$post_map$high_area, sp.obj)
```
